Quarto Shiny ALM

### 2023-05-25 Model/htw_exam.qmd
test sync

---
title: ALM & EXAM Fitting
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: false
editor: 
  markdown: 
    wrap: 72
---

@@

```{r}
#| code-fold: show
pacman::p_load(tidyverse,data.table)
options(dplyr.summarise.inform=FALSE)

d <- readRDS('dPrune-01-19-23.rds')

>>>>

---
title: ALM & EXAM Fitting
date: last-modified
categories: [Modeling, ALM, R]
page-layout: full
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: false
editor: 
  markdown: 
    wrap: 72
---

@@

```{r}
#| code-fold: show
pacman::p_load(tidyverse,data.table,here)
options(dplyr.summarise.inform=FALSE)

d <- readRDS(here("data/dPrune-01-19-23.rds"))

### 2023-05-25 Visuals_Interactives/quarto_shiny.qmd
test sync

---
#title: Quarto Shiny ALM
format: 
  html:
    highlight-style: a11y-dark
    page-layout: custom
    # grid:
    #   sidebar-width: 10px
    #   body-width: 1200px
    #   margin-width: 10px
    #   gutter-width: 1.5rem
server: shiny
#toc: true
execute: 
  warning: false
code-fold: true
code-tools: true
---

>>>>

---
title: Quarto Shiny ALM
date: last-modified
categories: [Simulation,ALM,EXAM,Shiny, R]
format: 
  html:
    highlight-style: a11y-dark
    page-layout: custom
    # grid:
    #   sidebar-width: 10px
    #   body-width: 1200px
    #   margin-width: 10px
    #   gutter-width: 1.5rem
server: shiny
#toc: true
execute: 
  warning: false
code-fold: true
code-tools: true
---
